---
title: "Key Performance Indicators for the USAID TUJITEGEMEE Project"
author: Roy Lennic Mwavita (MEAL Officer, CIPK)
output:
  slidy_presentation: default
  ioslides_presentation: default
date: "`r Sys.Date()`"
abstract: >
  This presentation covers the key performance indicators (KPIs) for the USAID TUJITEGEMEE Project. The KPIs are used to evaluate the project's progress and impact on the targeted communities.
keywords: ["USAID", "TUJITEGEMEE Project", "Key Performance Indicators", "CIPK", "MEAL"]
editor_options: 
  chunk_output_type: console
---

# Introduction

The USAID TUJITEGEMEE Project aims to improve the lives of Orphans and Vulnerable Children (OVC) by addressing their needs through various interventions. This presentation provides an overview of the key performance indicators (KPIs) used to measure the project's success.

# Objectives

- To evaluate the impact of the project on the targeted communities.
- To identify gaps in service delivery and areas for improvement.
- To track progress against set targets.

# Data Sources

The data for this analysis was collected from various reports downloaded from the 
Child Protection Information Management System (CPIMS) and PIMS, including:

<div style="display: flex; justify-content: space-around;">

<div style="flex: 1; padding: 10px;">
**CPIMS REPORTS**
- Registration List Report
- Case Plan Report
- Benchmark Report
- List of OVC Served Report
- Caregivers Served Report
- HIV Risk Screening Report
- Viral Load Report
</div>

<div style="flex: 1; padding: 10px;">
**PIMS REPORTS**
- Caregiver DCF Report
- Group Membership Report
- Loan Tracker Report
- On Path to Graduation Report
- Ready to Graduate Report
- Referral Report
- HIV Management Report
- HEI Tracking Report
- CBIM Register Report
- CBIM Sessions Report
- CBIM Survey Report
- Sinovuyo Register Report
- Teen Report
- Sinovuyo Sessions Report
</div>

</div>

# Analysis Methodology

The analysis was conducted using R and includes data wrangling, summary statistics, and visualizations. Key performance indicators were calculated for different interventions and compared against targets.

---

```{r Import Packages, echo=FALSE, warning=FALSE}
library(pacman)
pacman::p_load(tidyverse, janitor, readxl, writexl, openxlsx, DT, kableExtra, here,
               tidylog)
```

```{r Import Datasets, warning=FALSE, include=FALSE, results='hide'}
##cpims data sets----------------------------------------------------------------

reglist <- read_excel(here("RegistrationListReport_01082024.xlsx"))
caseplan <- read_excel(here("CasePlanReport_01082024.xlsx"))
benchmarkreport <- read_excel(here("BenchmarkReport_01082024.xlsx"))
loos <- read_excel(here("ListOfOvcServedReport_01082024.xlsx"))
caregiverserved <- read_excel(here("CaregiversServedReport_01082024.xlsx"))
riskscreening <- read_excel(here("HivRiskScreeningReport_01082024.xlsx"))
vl <- read_excel(here("ViralLoadReport_01082024.xlsx"))

##pims data sets-----------------------------------------------------------------

caregiverdcf <- read_excel(here("caregiver_dcf__20240801071514.xlsx"))
groupmembership <- read_excel(here("group_membership_regdatatables_20240801.xlsx"))
loantracker <- read_excel(here("loan_tracker__20240801071509.xlsx"))
onpathtograduation <- read_excel(here("onpathtograduation_20240801.xlsx"))
readytograduate <- read_excel(here("readytograduate_20240801.xlsx"))
referral <- read_excel(here("referral_20240801.xlsx"))
hivmanagementReport <- read_csv(here("HIVManagementReport_20240801.csv"))
heitracking <- read_excel(here("heitracking_20240801.xlsx"))
cbimregister <- read_excel(here("cbimregister_20240801.xlsx"))
cbimsessions <- read_csv(here("cbimsessions_20240801.csv"))
cbimsurvey <- read_csv(here("cbimsurvey_20240801.csv"))
sinovuyoregister <- read_excel(here("sinovuyoregister_20240801.xlsx"))
caregiverassesmentreport <- read_csv (here("caregiverassesmentreport_20240801.csv"))
teen <- read_csv(here("teen_20240801.csv")) 
sinovuyosessions <- read_csv(here("sinovuyosessions_20240801.csv"))

```


```{r COP23 Targets, warning=FALSE, include=FALSE, results='hide'}
cop_target_sw <- data.frame(case_manager = c('Dave Mainga', 'Abdulnasir Mohammed',
                                            'Ummu Bwanamkuu', 'Armon Thinga'),
                         target = c(956, 1229, 1044, 1349)) %>% 
  rename('COP 23 Target' = 'target') %>% 
  adorn_totals('row')

sinovuyo_target_sw <- data.frame(case_manager = c('Dave Mainga', 'Abdulnasir Mohammed',
                                                 'Ummu Bwanamkuu', 'Armon Thinga'),
                              target = c(118, 156, 126, 169)) %>% 
  rename('Sinovuyo Target' = 'target') %>% 
  adorn_totals('row')

cbim_target_sw <- data.frame(case_manager = c('Dave Mainga', 'Abdulnasir Mohammed',
                                             'Ummu Bwanamkuu', 'Armon Thinga'),
                          target = c(92, 121, 97, 130)) %>% 
  rename('CBIM Target' = 'target') %>% 
  adorn_totals('row')

graduation_target_sw <- data.frame(case_manager = c('Dave Mainga', 'Abdulnasir Mohammed',
                                                   'Ummu Bwanamkuu', 'Armon Thinga'),
                                target = c(320, 428, 266, 362)) %>% 
  rename('Graduation Target' = 'target') %>% 
  adorn_totals('row')

#targets by constituency------------------------------------

cop_target <- data.frame(constituency = c('Kilifi North', 'Malindi'),
                           target = c(3229, 1349)) %>% 
  rename('COP 23 Target' = 'target') %>% 
  adorn_totals('row')

sinovuyo_target <- data.frame(constituency = c('Kilifi North', 'Malindi'),
                                target = c(400, 169)) %>% 
  rename('Sinovuyo Target' = 'target') %>% 
  adorn_totals('row')

cbim_target <- data.frame(constituency = c('Kilifi North', 'Malindi'),
                            target = c(310, 130)) %>% 
  rename('CBIM Target' = 'target') %>% 
  adorn_totals('row')

graduation_target <- data.frame(constituency = c('Kilifi North', 'Malindi'),
                                  target = c(1014, 362)) %>% 
  rename('Graduation Target' = 'target') %>% 
  adorn_totals('row')

total_targets <- cop_target_sw %>% 
  left_join(sinovuyo_target_sw) %>% 
  left_join(cbim_target_sw) %>% 
  left_join(graduation_target_sw) %>% 
  adorn_totals('col') %>% 
  select(case_manager, Total) %>% 
  rename('Total Targets' = 'Total') 
```


# COP 23 Targets

The COP 23 targets are the President's Emergency Plan for AIDS Relief (PEPFAR) Country Operational Plan 2024
for the USAID Tujitegemee Project. These targets often involve key performance indicators (KPIs) such as:

- OVC_SERV
- OVC_HIVSTAT

```{r data-processing, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
total_targets_table <- cop_target_sw %>% 
  left_join(sinovuyo_target_sw) %>% 
  left_join(cbim_target_sw) %>% 
  left_join(graduation_target_sw) %>% 
  adorn_totals('col') %>% 
  rename('Total Targets' = 'Total',
         'Case Manager' = 'case_manager')
```

# COP 23 Targets for each Case Manager
The table below displays the COP23 Targets for each Case Manager implementing USAID TUJITGEMEE project
in Kilifi North and Malindi Sub County under Council of Imams and Preachers of Kenya (CIPK).


```{r display-table, echo=FALSE}
total_targets_table %>% 
  kableExtra::kable(align = c("l", rep("c", ncol(total_targets_table) - 1))) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "bordered"), 
                font_size = 18, 
                position = "center") %>% 
  column_spec(1, width = "3in", background = "lightyellow") %>% 
  row_spec(nrow(total_targets_table), background = "lightyellow")
```
